---
title: Jordan Peterson is a Brave Political Philosopher
author: ~
#date: '2022-05-14'
date: "`r format(Sys.time(), '%Y-%m-%d')`"
slug: jordan-peterson-is-a-brave-political-philosopher
categories: ["Politics"]
tags: ["politics", "freedom"]
bibliography: ../../../static/bibliography.bib
csl: ../../../static/citations/apa-no-initials.csl
link-citations: true
reference-section-title: References
---
```{r setup, include = FALSE}
library(blogdown)
```

Jordan Peterson is a Canadian clinical psychologist that is now known for his counter-narrative political views.
He became famous after standing up against [Bill C-16](https://www.parl.ca/DocumentViewer/en/42-1/bill/c-16/first-reading) which forces compelled speech.
He is also mainly known for criticizing the radical left.
He is often described as conservative by the right.
However, just because he criticizes left-wing extremists, does not mean he is a conservative
He said in an interview that he's "no right-winger".

```{r jordarn-peterson-no-right-winger}
shortcode("youtube", "1OeWGMr_tns")
```

# Bill C-16

Bill C-16 is a bill passed by the Parliament of Canada titled *An Act to amend the Canadian Human Rights Act and the Criminal Code*.
It states that "gender identity and expression" are prohibited grounds of discrimination.
Freedom of speech does not exist in Canada because of laws like this.
The Canadian Charter of Rights and Freedoms states that Canadian citizens have the right to freedom of expression [@canadian-charter-of-rights-and-freedoms].
But Bill C-16 violates this fundamental human right.
By enforcing compelled speech, Canada violates the right to freedom of expression.
These are two contradicting texts in the Charter of Rights.
They cannot both be true at the same time.
This is called "doublethink" in *Nineteen Eighty-Four*.

Jordan Peterson uploaded YouTube videos criticizing Bill C-16.
He protested at the University of Toronto because he does not want to use made-up, narcissistic gender pronouns.
He knows that any attack on freedom of speech is dangerous.
Radical leftists proceeded to vandalize his property.
They did not receive any legal punishments because they are "politically correct."
These are the same people that complain about "privilege."
They destroyed his speaker, making his microphone useless.
This was an obvious attempt to silence him and to provoke him into doing something violent.
However, it only made him louder and more composed.
He proceeded to yell like a bad-ass instead of speaking into his microphone.

```{r jordan-peterson-uot}
shortcode("youtube", "HAlPjMiaKdw")
```

# Making Him Stronger

All of the radical left's attempts to attack Jordan Peterson only make him stronger.
He is a clinical psychologist so of course he knows the psychology of the people who attack him.
These people do not want any productive actions to occur.
They only want to provoke people into doing stupid things so that they can continue to play the [victim card](https://www.urbandictionary.com/define.php?term=victim card).
Sometimes these attempts are successful and sometimes they are not.
They are successful against most inexperienced people.
However, against politicians and psychologists, they are never successful.
The best way to defeat radical leftists is to let them defeat themselves.

```{r elon-musk-far-left}
shortcode("twitter", user = "elonmusk", id = "1520017094007476224")
```

## McMaster University protest

```{r mcmaster-university-meltdown}
shortcode("youtube", "vMSmUzDt-7U")
```

Jordan Peterson proved this in McMaster University when a mob of social justice warriors attacked him.
They harassed and assaulted him.
They were using loud instruments in an attempt to irritate him.
They were yelling at him, but obviously what they said does not matter.
They were not there to protest, they were there to attack.
Instead of directly responding to these protesters, Jordan Peterson described their mentality as he is a psychologist. 
He talked about why he will not respond to them and what you should do if you end up in the same situation. 
The protesters did not even hear him because they made too much noise.
They purposefully deafened themselves.
But if they actually listened, they would understand that he was making solid points.
This reminds me of the "Two Minutes Hate" from *Nineteen Eighty-Four*:

```{r two-minutes-hate}
shortcode("youtube", "XvGmOZ5T6_Y")
```

# Freedom Convoy

Beginning in early 2022, the Freedom Convoy is a series of protests against COVID-19 mandates.
It is mainly about vaccine and mask mandates.
They have had enough of the lies of the Liberal Government.
In the beginning of the COVID-19 pandemic, Prime Minister Justin Trudeau said we need "two weeks to flatten the curve."
Well Mister Trudeau, it has been over two years.
I think you either made a slight miscalculation, or you are a tyrannical dictator who wants to violate our Charter rights by stealing medical freedom from Canadians.
I wonder which one it is 🤔.

```{r justin-trudeau-two-weeks-to-flatten-the-curve}
shortcode("youtube", "NVYMfvZ-R18")
```

Jordan Peterson showed support for the Freedom Convoy.
He also showed disgust at Justin Trudeau for his hypocrisy.
With the help of him and some other influencers, the Freedom Convoy was able to achieve some of its goals.
Most provinces in Canada have already removed their vaccine and mask mandates.
Many people—like myself—have decided to still not comply with these mandates even where they do exist.
The movie is over, and we are about to exit the cinema.
Some people do not fall for the fear-mongering anymore.

# Conclusion

Jordan Peterson has talked about many things other than Bill C-16 and the Freedom Convoy.
But these are the things that I like him the most for.
He is not afraid to counter the mainstream narrative.
For that, he should be applauded,
Doctors, lawyers, teachers, psychologists, and other intelligent people will submit to the mainstream narrative.
Jordan Peterson will never do that
