---
title: Programming is Invaluable for Everyone
date: '2022-05-06'
slug: programming-is-invaluable-for-everyone
tags: ["programming"]
bibliography: ../../../static/bibliography.bib
csl: ../../../static/citations/apa-no-initials.csl
link-citations: true
reference-section-title: References
---
```{r setup, include = FALSE}
library(blogdown)
```

Most people view programming as something that only a specific type of people are able to do and should do.
This specific type of person is portrayed as a genius; smarter than everyone else.
This means that they think most normal people are unable to learn programming because they are not smart enough.
But since they do not want to learn it themselves, they make the excuse that it is not important for them.
It does not require smartness to learn programming, it only requires time, desire, and effort.

# Time

A common excuse for dozens of things outside of programming is "I don't have enough time."
Most people who say this really mean to say "I don't want to do this."
If someone really does not have enough time, that means they spend the entire day only doing things they must do.
This is almost never the case though.
Most people have enough time to use social media, watch movies, play games, and other unproductive things.
Most people come home from school or work tired, so it is no surprise that they spend their time doing unproductive things. 

```{r}
shortcode("youtube", "RHErQ5l6Jss")
```

This video of Floyd Mayweather proves that most adults have four hours of spare time.
You could spend only one hour every day to learn programming and easily become talented at it.
You would still have three more hours to spend time with your family and do other things.
You should not use your tiredness and previous hard work as an excuse to prevent you from doing great things.
Rather, it should only motivate you more.
If you can spend nine hours every day working for a company, you can spend one hour every day working for yourself.

Programming seems like it requires more than one hour a day of practice to become good at.
This depends on the type of language.
Most markup languages are surprisingly easy to learn.
For example, it takes about ten minutes to learn the basics of Markdown.
Almquist shells are not as easy to learn as markup languages, but their syntax is also easy for English readers to understand.
To become good at writing shell scripts, it just takes a little bit of practice.
High-level programming languages like Python are slightly more difficult to learn than almquist shells but also many times less valuable.
I avoid learning these types of languages unless necessary.
Middle-level programming languages like C are difficult but manageable, and they are extremely valuable and fast.
Just like high-level languages, I would not recommend learning low-level languages unless absolutely necessary.

# Desire

You should absolutely desire learning programming before you actually do it.
Some people learning programming do not have a clue as to why they are and how it is important.
This is because schools tend to only teach **how** to do things in programming, and not **why** to do them.
The most important reason to code is to create programs that improve life in any way.
You should, for example, write a shell script that automatically does something that you would have to manually do every time.
The vast majority of my projects on [my GitHub page](https://github.com/amarakon) are simple shell scripts that I wrote for myself.

Even though I wrote them for myself, they are also there for anyone in the public to use for any reason.
This is the beauty of open-source software.
Open-source software makes programming much easier that it otherwise would be because you can easily look at anyone's code and learn how a program is made.
Understanding how programs are made is not only important for creating software, but for using it as well.
You will acquire a better taste of what makes good and bad software, and this will help you learn even further.
It will also further drive your desire, as you might want to create a type of program nobody has created before or change something in the industry.

Programming makes you look smarter than you actually are.
Since it does not specifically require intelligence to code—but it seems that way, programming makes you look "nerdy" in a good way.
To speak in detail about certain programming terms that others will not understand certainly makes you look smart.
Try not to deter anyone else from learning to do so themselves though.
It is something that should definitely be added to your resume to improve your job opportunities.

# Effort

When programming, you should put in actual effort to do so.
Some people may have the time and desire but not the effort.
They might want to program to quickly get a software engineering job and make money.
This is wrong because it is not the right reason to program.
The right reason to program is to improve everyday life.
Program for yourself and others before you program for money.

Respectfully, you should program with the right tools.
It does not make sense to be a programmer and simultaneously use bad software—that is hypocritical.
Do not use any version of Windows as your main operating system.
Windows 10 and below do not even have a proper shell, while Windows 11 shamelessly and disgracefully copied Linux [@wsl-documentation] and KDE Plasma [@windows-kde-plasma].
Wix is an abysmal website builder that does not even function properly and is ugly and extremely limited.
You should be programming on Linux.
You should be creating websites by coding in HTML, CSS, and JavaScript, or by using an R package.
In order to actually be a valuable programmer, you need to create an environment where you can create good programs.
If you refuse to create such an environment, you refuse to put in the effort, programming becomes worthless.

If you are putting in the correct amount of effort, programming should come naturally to you.
You should not be reminding yourself to be programming, but it should come naturally with the things you want to do.
For example, I naturally always improve this website by putting in my effort.
I know that my website is useful and valuable, so I update it every day.
If my website was useless and worthless, I would not care about it.
When schools teach computer science, they do not teach the programs' uses and values, causing their students to be lost.
Along with programming you should follow a programming philosophy, like [free software philosophy](https://www.gnu.org/philosophy/philosophy.en.html).
